%Michael Mosher's Resume
%Created: Sept, 2014
%Updated: Feb, 2018
\documentclass[11pt]{article}
\usepackage{xcolor}
\usepackage{helvet}
\usepackage[absolute]{textpos}
\usepackage{geometry}
\usepackage{multicol}
\usepackage[framemethod=TikZ]{mdframed}
\pagestyle{empty}
\geometry{letterpaper,tmargin=1.2in,bmargin=0.5in,lmargin=1.25in,rmargin=1.25in,headheight=0in,headsep=0in,footskip=.3in}
\renewcommand{\labelitemi}{\bf--}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\newenvironment{resblock}[1]
  {\noindent{\Large\textbf{#1}}}
  {\par\vspace{1em}}
\begin{document}
\include{title}
%
%\begin{resblock}{Profile}\par
%  \hangindent=1.5em
%  \hangafter=1
%A flexible, reliable hospitality employee seeking to change industries and contribute logical reasoning, critical thinking, and persuasive communicating to improve the overall success and efficiency of a team.
%\end{resblock}

\begin{resblock}{Achievements}\par
  \begin{changemargin}{0em}{0em}
  \begin{itemize}
    \item[$\circ$]Prepared materials for \textbf{coaching clients to DevOps success}
    \item[$\circ$]\textbf{Developed a Slack bot} to stimulate a "ChatOps" culture
    \item[$\circ$]Created monitoring dashboards to \textbf{visualize service level indicators}
    \item[$\circ$]\textbf{Implemented a solution to synchronize time tracking} across multiple platforms
  \end{itemize}
  \end{changemargin}
\end{resblock}
%\resline{2.575in}

\begin{resblock}{Work Experience}
\vspace{0.6em}

  \textbf{System Administrator}, SpinDance\hfill August 2014--present\strut\hrule
  \begin{changemargin}{3em}{0em}
    \textbf{Leadership}---Providing DevOps mentoring to teammates and associates. Evaluating automation tools and establishing best practices for using them.

    \textbf{Automation}---Managing dozens of services on 100+ servers using Chef. Configuring continuous integration for 50+ repositories using Jenkins and TravisCI. Driving Terraform adoption to automate provisioning, as well.
    
    \textbf{Monitoring}---24/7 on-call support for production servers. Quickly triaging issues to maintain service level objectives.
  \end{changemargin}

  \textbf{Setup Crew}, Prince Conference Center\hfill October 2007--September 2013\strut\hrule
  \begin{changemargin}{3em}{0em}
%    \textbf{Versatility}---Set up tables, chairs, and A/V equipment, including laptops, microphones, speakers, and recording equipment; cleaned public areas; drove airport shuttles; trained to work at the Front Desk
%
    \textbf{Customer Service}---Learned to anticipate client demands in order to provide them with an ideal working experience.

    \textbf{Independence}---Frequently worked with little or no supervision and was complimented on my thoroughness and work ethic.
  \end{changemargin}
\end{resblock}
%\resline{6.475in}

%\setlength\multicolsep{0pt}
\begin{resblock}{Skills} % these can be turned on and off depending on job opening
  \begin{multicols}{3}\begin{flushleft}\begin{itemize}
%    \item[$\circ$]SEXY
    \item[$\circ$]Linux \mbox{administration}
    \item[$\circ$]BASH scripting
    \columnbreak
    \item[$\circ$]Release Engineering
    \item[$\circ$]Databases% \& SQL Server
%    \item[$\circ$]Containerization with Docker
    \columnbreak
%    \item[$\circ$]Creating scripts and tools with Ruby
%    \item[$\circ$]Test-driven development with RSpec and Mocha
%    \item[$\circ$]Python Scripting
%    \item[$\circ$]Rails Support
%    \item[$\circ$]PHP Support
    \item[$\circ$]TypeScript
    \item[$\circ$]Elm
%    \item[$\circ$]HTML5 \& CSS3
  \end{itemize}\end{flushleft}\end{multicols}
\end{resblock}

%\resline{7.85in}
\begin{resblock}{Education \& Certification}
\vspace{1em}

  \textbf{Amazon Web Services}\strut\hrule
    \begin{changemargin}{3em}{0em}
      \textbf{Certified Solutions Architect}---Associate\hfill June 2017

      \textbf{Certified SysOps Administrator}---Associate\hfill July 2017
    \end{changemargin}
  
  \textbf{Calvin College}, Grand Rapids MI\strut\hrule
  \begin{changemargin}{3em}{0em}
    \textbf{Bachelor of Arts}---Mathematics \& Philosophy\hfill May 2011

    Excelled in courses on programming and logic.
  \end{changemargin}
\end{resblock}

%\resline{9.65in}
\begin{resblock}{Additional Skills}
\vspace{1em}

    \textbf{Saxophone}---Alto \& Tenor, 10+ years experience

    \textbf{Woodworking}---$<$1 year experience

\end{resblock}
\end{document}
